The Chemistry Development Kit (CDK): atom typing, rendering, molecular formulas, and substructure searching

### 2016-10-09 article.tex
Done

  \subsection*{Table 3 - The molecular fingerprints in CDK.}
  \label{tab:fingerprints}
  Listed are the currently available molecular fingerprint in CDK with
  information about whether they come as bit / count versions, what CDK version
  they appeared in, their default size and where applicable also relevant
  references.
  \vskip 1\baselineskip

    \begin{minipage}{1\textwidth}
    \renewcommand*{\thempfootnote}{\fnsymbol{mpfootnote}}
    \centering
    \begin{tabular}{lcclc}
                             & Bit version  & Count version & CDK version & Default Size    \\
  CircularFingerprinter~\cite{rogers2010extended, Clark2014}      & $\checkmark$ & $\checkmark$  & \cdkversion{}     & $1\,024$ / $2^{32}$%
\footnote[1]{For the CircularFingerprinter the bit version is folded to 1024 whereas the count version is unfolded.} \\
  EStateFingerprinter~\cite{Hall1995}       & $\checkmark$ &               & 1.2.0       & $79$            \\
  ExtendedFingerprinter      & $\checkmark$ &               & 1.0         & $1\,024$        \\
  Fingerprinter              & $\checkmark$ &               & 1.0         & $1\,024$        \\
  GraphOnlyFingerprinter     & $\checkmark$ &               & 1.0         & $1\,024$        \\
  HybridizationFingerprinter & $\checkmark$ &               & 1.4.0       & $1\,024$        \\
  KlekotaRothFingerprinter~\cite{Klekota2008}   & $\checkmark$ &               & 1.4.6       & $4\,860$        \\
  LingoFingerprinter~\cite{vidal2005lingo}         & $\checkmark$ &               & \cdkversion{}     & NA%
\footnote[2]{The Lingofingerprinter does not have a default size.}
                                                                                             \\
  MACCSFingerprinter         & $\checkmark$ &               & 1.2.0       & $166$           \\
  PubchemFingerprinter~\cite{pubchemFP}       & $\checkmark$ &               & 1.4.0       & $881$            \\
  ShortestPathFingerprinter  & $\checkmark$ &               & \cdkversion{}     & $1\,024$        \\
  SignatureFingerprinter~\cite{signaturefingerprints}     & $\checkmark$ & $\checkmark$  & \cdkversion{}     & $2^{32}$         \\
  SubstructureFingerprinter  & $\checkmark$ &               & 1.0         & $307$           \\

>>>>

  \subsection*{Table 3 - The molecular fingerprints in CDK.}
  \label{tab:fingerprints}
  Listed are the currently available molecular fingerprint in CDK with
  information about whether they come as a bit and/or count version, what CDK version
  they were introduced in, their default size, and relevant
  references, where applicable.
  \vskip 1\baselineskip

    \begin{minipage}{1\textwidth}
    \renewcommand*{\thempfootnote}{\fnsymbol{mpfootnote}}
    \centering
    \begin{tabular}{lcclc}
                             & Bit version  & Count version & CDK version & Default Size    \\
  CircularFingerprinter~\cite{rogers2010extended, Clark2014}      & $\checkmark$ & $\checkmark$  & \cdkversion{}     & $1\,024$ / $2^{32}$%
\footnote[1]{For the CircularFingerprinter the bit version is folded to 1024 whereas the count version is unfolded.} \\
  EStateFingerprinter~\cite{Hall1995}       & $\checkmark$ &               & 1.2.0       & $79$            \\
  ExtendedFingerprinter      & $\checkmark$ &               & 1.0         & $1\,024$        \\
  Fingerprinter              & $\checkmark$ &               & 1.0         & $1\,024$        \\
  GraphOnlyFingerprinter     & $\checkmark$ &               & 1.0         & $1\,024$        \\
  HybridizationFingerprinter & $\checkmark$ &               & 1.4.0       & $1\,024$        \\
  KlekotaRothFingerprinter~\cite{Klekota2008}   & $\checkmark$ &               & 1.4.6       & $4\,860$        \\
  LingoFingerprinter~\cite{vidal2005lingo}         & $\checkmark$ &               & \cdkversion{}     & NA%
\footnote[2]{The LingoFingerprinter does not have a default size.}
                                                                                             \\
  MACCSFingerprinter         & $\checkmark$ &               & 1.2.0       & $166$           \\
  PubchemFingerprinter~\cite{pubchemFP}       & $\checkmark$ &               & 1.4.0       & $881$            \\
  ShortestPathFingerprinter  & $\checkmark$ &               & \cdkversion{}     & $1\,024$        \\
  SignatureFingerprinter~\cite{signaturefingerprints}     & $\checkmark$ & $\checkmark$  & \cdkversion{}     & $2^{32}$         \\
  SubstructureFingerprinter  & $\checkmark$ &               & 1.0         & $307$           \\
